\documentclass{beamer}
\usetheme{Berlin}
\usefonttheme{serif}

\setbeamercolor{frametitle}{bg=black,fg=white}
\setbeamercolor{title}{bg=black,fg=white}
\setbeamercolor{section in head/foot}{bg=brown,fg=white}
\setbeamercolor{subsection in head/foot}{bg=brown,fg=white}
\setbeamercolor{navigation symbols}{fg=brown}
\setbeamercolor{normal text}{fg=black}

\fontsize{14}{16}\selectfont
\fontseries{b}\selectfont

\usepackage{fbox}
\setlength{\fboxrule}{1pt}
\setlength{\fboxsep}{0pt}

\usepackage{shadow}

\title{WordVerse Project Overview}
\subtitle{}
\author{\bfseries Sheetal Lodhi \and \bfseries Sonakshi Raj }
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\section{Introduction}

\begin{frame}{\bfseries Introduction}
    \begin{itemize}
        \item \bfseries WordVerse is a web application designed for playing the Wordle game.
        \item \bfseries We've got two awesome modes for you: 'Guess My Word' where you try to figure out a mystery word, and 'I'll Guess Yours' where our chatbot tries to read your mind
    \end{itemize}
\end{frame}

\section{Project Motivation}

\begin{frame}{\bfseries Why WordVerse?}
    \begin{itemize}
        \item \bfseries WordVerse is an interactive game that requires real-time communication between the client and server. This makes it an ideal project for learning WebSockets, which enable bi-directional communication between the client and server
        \item \bfseries It offers us a opportunity to learn golang. 
\end{frame}

\section{Key Features}

\begin{frame}{\bfseries Key Features of WordVerse}
    \begin{itemize}
        \item \bfseries Classic Wordle game.
        \item \bfseries NPC Character (bot) that interacts with users and assists in gameplay.
        \item \bfseries Responsive design optimized for different devices.
        \item \bfseries Real-time communication using WebSocket.
        \item \bfseries Backend implemented in Go.
        \item \bfseries User-selected secret word functionality.
    \end{itemize}
\end{frame}

\section{Technologies Used}

\begin{frame}{\bfseries Technologies and Tools}
    \begin{itemize}
        \item \bfseries Frontend: React, CSS.
        \item \bfseries Backend: Go, WebSocket.
        \item \bfseries Libraries: LaTeX, Gin.
    \end{itemize}
\end{frame}

\section{Project Challenges}

\begin{frame}{\bfseries Overcoming Challenges}
    \begin{itemize}
        \item \bfseries Learning and mastering React for frontend development.
        \item \bfseries Implementing real-time communication using WebSocket.
        \item \bfseries Integrating the NPC character (bot) with custom logic.
        \item \bfseries Setting up and configuring the Go backend with WebSocket.
    \end{itemize}
\end{frame}

\section{Proud Achievements}

\begin{frame}{\bfseries Proud Moments}
    \begin{itemize}
        \item \bfseries Custom-built NPC character (bot) with unique interaction logic.
        \item \bfseries Efficient and clean file structure that made the project easy to manage.
        \item \bfseries Successfully implementing real-time communication, enhancing user interaction.
        \item \bfseries The successful deployment of the project and the positive feedback received.
    \end{itemize}
\end{frame}

\section{File Structure Overview}

\begin{frame}{\bfseries Understanding the File Structure}
    \begin{itemize}
        \item \bfseries Frontend Directory:
            \begin{itemize}
                \item \bfseries src/components: Contains React components.
                \item \bfseries src/botcomponents: Special components related to the NPC bot.
                \item \bfseries App.js: Entry point of the React application.
                \item \bfseries index.js: Main file for rendering the app.
                \item \bfseries websocket.js: Handles WebSocket connections.
            \end{itemize}
        \item \bfseries Backend Directory:
            \begin{itemize}
                \item \bfseries main.go: Entry point for the backend server.
                \item \bfseries words.txt: Contains the list of words for the game.
                \item \bfseries go.mod/go.sum: Dependency management for Go.
            \end{itemize}
    \end{itemize}
\end{frame}

\section